---
title: "p8105_hw6_yh3554"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(dbplyr)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1
To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

## Problem 2

#### Read the data

```{r}
homicide_df = read_csv("data_homicide/homicide-data.csv", show_col_types = FALSE)
```

#### Table of proportion of missing data

```{r}
homicide_df %>% 
  summarise_at(vars(lat:disposition), .funs = function(x) mean(is.na(x))) %>%
  knitr::kable()
```

#### Describle the raw data

The `homicide_df` is data contains homicides in 50 large U.S. It has `r nrow(homicide_df)` variables and `r ncol(homicide_df)` cases. The key variables are unique id, victim demographic information (first name, last name, age, sex), the location (city, state, latitude, longitude), and disposition. It has `r sum(is.na (homicide_df$lat))` missing latitude information and `r sum(is.na (homicide_df$lon))` missing longitude information.

#### Generate new variables

Create a city_state variable, and a binary variable indicating whether the homicide is solved. Also omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO (these don’t report victim race), and Tulsa, AL (a data entry mistake). Limit analysis those for whom victim_race is white or black. Be sure that victim_age is numeric. Cannot convert victim_age to numeric variable since there is unknown age, so drop the unknown, then use `as.numeric` to convert it.
* victim_sex: male, female
* status: homicide case status whether it is solved
```{r}
homicide_df_new <- homicide_df %>%
  filter(!victim_age == "Unknown", 
         victim_race == "White" | victim_race == "Black") %>%
  mutate(victim_age = as.numeric(victim_age),
         city_state = str_c(city, state, sep = ", "),
         status = ifelse(disposition == "Closed without arrest", "unsolved", "solved"),
         ) %>%
  filter(!city_state == "Dallas, TX", !city_state == "Phoenix, Ax", 
         !city_state == "Kansas City, MO", !city_state == "Tulsa, AL") %>%
  mutate(victim_race = as.factor(victim_race),
         victim_sex = factor(victim_sex, level = c("Male", "Female", "Unknown")),
         status = factor(status, level = c("solved", "unsolved")))

head(homicide_df_new)
summary(homicide_df_new)
```

